### 2023-04-12 my_paper/Hadah-last-names.tex
some edits

To retrieve the effect of having a Hispanic last name, I compare the children of inter-ethnic marriages between Whites and Hispanics. I find that while men born to White father-Hispanic mothers earn less than men born to Hispanic father-White mothers, this gap is entirely explained by educational differences. Thus, I do not find a significant effect of having a Hispanic last name. Finally, I find that men identifying as Hispanic earn significantly less than those who do not, even when I control ancestry and education.

@@

In columns (v) and (vi), I calculate the differences in means between HH-WW (column v) and HW-WH (column vi). Overall, HH children do worse than WW children. HH has one less year of education compared to WW, 2.1 percentage points less likely to be employed, HH men earn 16.4\% less than WW men, and HH women make 12.3\% less than WW women. Therefore, these two groups, HH and WW, are different in many observable.

@@

Let $Y_{it}$ be the annual log earnings of person $i$ at time $t$. $WH_{i}$, $HW_{i}$ and $HH_{i}$ are indicator variables for the type of parents person $i$ has. $X_{it}$ is a vector of controls, $\gamma_{t}$ are year fixed effects and $\phi_{it}$ represents the error term. The equation for this strategy is written as follows:
\begin{equation} \label{eq:1a}
Y_{it} = \beta_{1} WH_{i} +\beta_{2} HW_{i} + \beta_{3} HH_{i} + X_{it} \pi + \gamma_{t}+\phi_{it}
\end{equation}

@@

Let $Y_{it}$ be the annual log earnings of person $i$ at time $t$. $WH_{i}$, $HW_{i}$ and $WW_{i}$ are indicator variables for the type of parents person $i$ has. $X_{it}$ is a vector of controls, $\gamma_{t}$ are year fixed effects and $\phi_{it}$ represents the error term. The addition to the previous model is the $Hispanic_{i}$ indicator variable. $Hispanic_{i}$ is equal to one if a person identifies as Hispanic and zero otherwise. I interact this term with the $WH_{i}$, $HW_{i}$ and $HH_{i}$.  The regression is presented in the following equation.

\begin{align} \label{eq:iden}
Y_{it} &= \beta_{1} HW_{i} +  \beta_{2} WH_{i} + \beta_{3} HH_{i} +\\
& \beta_{4} WH_{i} \cdot Hispanic_{i} + \beta_{5} HW_{i}\cdot Hispanic_{i} +  \beta_{6} HH_{i} \cdot Hispanic_{i}+ \nonumber \\
&X_{it} \pi + \gamma_{t}+\phi_{it} \nonumber
\end{align}

The coefficients of interest from equation \ref{eq:iden} are $\beta_{4}$, $\beta_{5}$ and $\beta_{6}$. The interaction terms capture the earnings gaps between members of $WH_{i}$, $HW_{i}$, and $WW_{i}$ that identify as Hispanic and White WW children.

@@

I find that the earnings gaps between WH and WW are 8.8\%, 14.1\% between HW and WW, and 16.1\% between HH and WW. Moreover, the difference in earnings between HW and WH children, that captures the effect of having a Hispanic last name, equals a statistically significant 5.3 percentage points. Meaning by comparing inter-ethnic children, a person with a Hispanic last name earns 5.3 percentage points less than someone with a White last name. However, more than half of the earnings gaps could be explained by educational differences between WW children and WH, HW, and HH. When I control for education, the gap between the three groups and WW is cut between by 50\% to 64.0\%. Furthermore, the last name effect decreases to a statistically insignificant 1.6 percentage points earnings gap.

I also find a significant earnings gap between those that identify as Hispanic and WW children. The gaps between WH, HW, and HH that identify as Hispanic and WW are, respectively, 13.4\%, 16.4\%, and 10.6\%. The difference between WH and HW that identify as Hispanic---captures the last name effect of those that identify as Hispanic--- is equal to 3 percentage points and is statistically insignificant. Controlling for education explains a big part of the gap. The gaps between WH, HW, and HH that identify as Hispanic and WW after controlling for education are 6.4\%, 10.8\%, and 6.2\%. The WH--WW and HH--WW gaps for those identifying as Hispanic become statistically insignificant after controlling for education. Finally, the difference between WH and HW that identify as Hispanic that identifies as Hispanic remains statistically insignificant but increases to 4.3 percentage points.

@@

I provide the results to the estimation of equation \ref{eq:1a} in table \ref{tab:lastnamereg}. The sample in this analysis includes full-time, full-year, and waged and salaried men, and I control for hours worked and age and include year fixed effects (FE). Column one in table \ref{tab:lastnamereg} is the results without controlling for education. Overall, there is big Hispanic--White earnings gaps. Children of White father-Hispanic mothers (WH) earn 8.8\% less than children of White fathers-White mothers (WW) families. The gap between children of Hispanic father-White mothers (HW) and WW children is 14.1\%. The gap between children of Hispanic father-Hispanic mothers (HH) and WW children is 16.1\%. Therefore, Hispanic children, inter-ethnic or children of homogeneous HH marriages, face a substantial earnings gap.

The difference between the estimates of WH and HW would capture the effect of having a Hispanic last name. A WH child will have a White last name since their father is White, while an HW child will have a Hispanic last name like their Hispanic father. When I take the difference between HW and WH, I find a statistically significant gap of 5.3 percentage points, which means that an inter-ethnic person with a Hispanic last name earns 5.3 percentage points less than a similar inter-ethnic person but with a White last name.

The literature on the earnings gaps shows that educational differences could explain a big part of these gaps \citep{duncan2006hispanics, duncan2017complexity, duncan2018identifying, duncan2020new}. Therefore, I run the equation \ref{eq:1a}, but this time I control for education. The regression results are in column two of table \ref{tab:lastnamereg}. The sample includes full-time, full-year, and waged and salaried men, and I control for hours worked and age and include year fixed effects (FE). The gap between WH and WW is 4.4\%, a reduction of 50\% from the baseline after controlling for education. The earning gaps between HW and HH, and WW were respectively reduced by 58\% and 64\%. After controlling for education, an HW man earns 5.9\% less than a WW man, and an HH man earns 5.8\% less. The effect of having a Hispanic last name on earnings decreased from 5.3 to 1.6 percentage points and became statistically insignificant after controlling for education.

Therefore, Hispanics face big earnings gaps compared to non-Hispanic Whites. By comparing the children of inter-ethnic marriages, I could study the impact of having a Hispanic last name on earnings. Having a Hispanic last name carries a cost in the labor market. A person with a Hispanic last name earns 5.3 percentage points less than someone with a White name. However, educational differences between Hispanics and Whites could explain more than 50\% of the earning gaps and all of the Hispanic last name costs.

@@

I run the estimating equation without controlling for education in table \ref{tab:identreg} column 1. I find that those that identify as Hispanic face a big earnings gap compared to those that do not. A WH man that identifies as Hispanic earns 13.4\% less than a WW man. An HW man who identifies as Hispanic makes 16.4\% less than a WW man, and an HH man who is determined as Hispanic earns 10.6\% less than a WW man. Comparing the coefficients of the interaction terms to those of the $WH_{i}$, $HW_{i}$, and $HH_{i}$ shows that members of the three groups that do not identify as Hispanic earn about the same as WW.
Moreover, the difference between $HW_{i} \cdot Hispanic_{i}$  and $WH_{i} \cdot Hispanic_{i}$ captures the effect of having a Hispanic last name and identifying as Hispanic compared to individuals who identify as Hispanic but have a White last name. A person with a Hispanic last name that identifies as Hispanic earns 3 percentage points less than a person that identifies as Hispanic but has a White last name. The difference between the two interaction terms is statistically insignificant.

In table  \ref{tab:identreg} column 2, I show the results of equation \ref{eq:iden} while controlling for education. Education explains all the identity costs for members of WH and HH. Also, controlling for education decreases the earnings gap for identifying as Hispanic and being a member of HW by 34.1\%. An HW member that identifies as Hispanic earns 10.8\% less than a WW man. Furthermore, the difference between $HW_{i} \cdot Hispanic_{i}$  and $WH_{i} \cdot Hispanic_{i}$ increases to 4.3 percentage points but remains statistically insignificant.

@@

 \begin{equation} \label{eq:naive}
 Y_{it} = \beta_{1} Hispanic_{i} + X_{it}^{\prime} + \gamma_{t}+\phi_{it}
 \end{equation}

Where $Y_{it}$ in equation \ref{eq:naive} is the annual log earnings of person $i$ at time $t$. $Hispanic_{i}$ is a dummy variable equal to one if person $i$ is Hispanic and zero otherwise. $X_{it}$ is a vector of controls, $\gamma_{t}$ is time fixed effects and $\phi_{it}$ is the error term.

@@

I compare the children of inter-ethnic marriages to study the labor market impact of having a Hispanic last name. The earning gap between WH and WW is 8.8\%, 14.1\% between HW and WW, and 16.1\% between HH and WW. When I compare the earnings of HW and WH children, which captures the effect of having a Hispanic last name, HW children earn 5.3\% less than WH children. Thus, by comparing inter-ethnic children, a person with a Hispanic last name makes 5.3\% less than someone with a White last name. Controlling for education, however, explains more than half of the earnings gaps between WW children and WH, HW, and HH. When I control for education, the gap between the three groups and WW is cut between 50-64.0\%. Furthermore, the last name effect decreases to a statistically insignificant 1.6\% earnings gap.

I also find that men who identify as Hispanic earn significantly less than those who do not, even when I control ancestry and education. The gaps between WH, HW, and HH that identify as Hispanic and WW are, respectively, 13.4\%, 16.4\%, and 10.6\%. Controlling for education explains a big part of the gap. The gaps between WH, HW, and HH that identify as Hispanic and WW after controlling for education are 6.4\%, 10.8\%, and 6.2\%.

@@

% $WH_{i}$ &  & -0.088{*}{*}{*} &  & -0.044{*}{*}{*} & \tabularnewline
%  &  & (0.018) &  & (0.017) & \tabularnewline
%  &  &  &  &  & \tabularnewline
% $HW_{i}$ &  & -0.141{*}{*}{*} &  & -0.059{*}{*}{*} & \tabularnewline
%  &  & (0.015) &  & (0.014) & \tabularnewline
%  &  &  &  &  & \tabularnewline
% $HH_{i}$ &  & -0.161{*}{*}{*} &  & -0.058{*}{*}{*} & \tabularnewline
%  &  & (0.008) &  & (0.007) & \tabularnewline
%  &  &  &  &  & \tabularnewline
% \midrule
% $HW_{i}$ - $WH_{i}$ &  & -0.053{*}{*} &  & -0.016 & \tabularnewline
%  &  & (0.024) &  & (0.022) & \tabularnewline
%  &  &  &  &  & \tabularnewline
% \midrule
% \textit{Controlling for:} &  &  &  &  & \tabularnewline
% Education &  & No &  & Yes & \tabularnewline
% Hours worked &  & Yes &  & Yes & \tabularnewline
% Age &  & Yes &  & Yes & \tabularnewline
% Year FE &  & Yes &  & Yes & \tabularnewline
% \bottomrule
% \end{tabular}

@@

% \begin{tabular}{lccccc}
% \hline 
%  &  & Log annual earnings &  & Log annual earnings & \tabularnewline
% Variables &  &  &  &  & \tabularnewline
% \hline 
%  &  &  &  &  & \tabularnewline
% $WH_{i}\times Hispanic_{i}$ &  & -0.134{*}{*} &  & -0.064 & \tabularnewline
%  &  & (0.053) &  & (0.049) & \tabularnewline
% $HW_{i}\times Hispanic_{i}$ &  & -0.164{*}{*}{*} &  & -0.108{*}{*} & \tabularnewline
%  &  & (0.052) &  & (0.048) & \tabularnewline
% $HH_{i}\times Hispanic_{i}$ &  & -0.106{*}{*} &  & -0.062 & \tabularnewline
%  &  & (0.049) &  & (0.045) & \tabularnewline
% $WH_{i}$ &  & 0.027 &  & 0.011 & \tabularnewline
%  &  & (0.048) &  & (0.045) & \tabularnewline
% $HW_{i}$ &  & 0.007 &  & 0.038 & \tabularnewline
%  &  & (0.050) &  & (0.046) & \tabularnewline
% $HH_{i}$ &  & -0.057 &  & 0.003 & \tabularnewline
%  &  & (0.057) &  & (0.044) & \tabularnewline
% \hline 
% $HW_{i}\times Hispanic_{i}$ - $WH_{i}\times Hispanic_{i}$ &  & -0.030 &  & -0.043 & \tabularnewline
%  &  & (0.074) &  & (0.068) & \tabularnewline
% \hline 
% \textit{Controlling for:} &  &  &  &  & \tabularnewline
% Education &  & No &  & Yes & \tabularnewline
% Hours worked &  & Yes &  & Yes & \tabularnewline
% Age &  & Yes &  & Yes & \tabularnewline
% Year FE &  & Yes &  & Yes & \tabularnewline
% \hline 
% \end{tabular}

%   \begin{tablenotes}
%    \item [\textit{Notes.}] This table includes the estimation results of equation \ref{eq:iden}.
%    \item [\textit{Notes.}] The four groups stand for White Husband White Wife (WW), White Husband Hispanic Wife (WH), Hispanic Husband White (HW), and Hispanic Husband Hispanic Wife (HH). $Hispanic_{i}$ is a dummy variable equal to one if a person identifies as Hispanic and zero otherwise.
%    \item [\textit{Notes.}] The sample is restricted to men working full-time full-year and are waged and salaried workers.
%     \item [\textit{Notes.}] Column one has the regression results when controlling for hours worked, age, and years of fixed effects. Column two has the results after controlling for education.
%   \end{tablenotes}
%   \end{threeparttable}
%   \end{adjustbox}
% \end{table}

@@

% \begin{tabular}{lccccc}
% \hline 
%  &  &  &  &  & \tabularnewline
% Variables &  & Log annual earnings &  & Log annual earnings & \tabularnewline
% \hline 
% $Hispanic_{i}$ &  & -0.156{*}{*}{*} &  & -0.060{*}{*}{*} & \tabularnewline
%  &  & (0.006) &  & (0.006) & \tabularnewline
% \textit{Controlling for:} &  &  &  &  & \tabularnewline
% Education &  & No &  & Yes & \tabularnewline
% Hours worked &  & Yes &  & Yes & \tabularnewline
% Age &  & Yes &  & Yes & \tabularnewline
% Year FE &  & Yes &  & Yes & \tabularnewline
% \hline 
% \end{tabular}

%   \begin{tablenotes}
%    \item [\textit{Notes.}] This table includes the estimation results of equation \ref{eq:naive}.
%    \item [\textit{Notes.}] $Hispanic_{i}$ is a dummy variable equal to one if a person identifies as Hispanic and zero otherwise.
%    \item [\textit{Notes.}] The sample is restricted to men working full time full-year and are waged and salaried workers.
%     \item [\textit{Notes.}] Column one has the regression results when controlling for hours worked, age, and fixed effects. Column two has the results after controlling for education.
%   \end{tablenotes}
%   \end{threeparttable}
%   \end{adjustbox}
% \end{table}

>>>>

To retrieve the effect of having a Hispanic last name, I compare the children of inter-ethnic marriages between Whites and Hispanics. I find that while men born to White father-Hispanic mothers earn less than men born to Hispanic father-White mothers, this gap is entirely explained by educational differences. Thus, I do not find a significant effect of having a Hispanic last name. Finally, I find that men identifying as Hispanic earn significantly less than those who do not, even when I control ancestry and education. Inter-ethnic children with a White father, and thus having a non-Hispanic last name, earn 14\% less than children of endogamous White parents. Inter-ethnic children with a Hispanic father, and thus having a Hispanic last name, earn 20\% less than children of endogamous White parents. Endogamous children with Hispanic parents earn 24\% less than children of endogamous White parents. A big part of the gaps could be explained by education. Inter-ethnic children with a White father and identify as Hispanic, and thus having a non-Hispanic last name, earn 14\% less than children of endogamous White parents. Inter-ethnic children with a Hispanic father and identify as Hispanic, and thus having a Hispanic last name, earn 18\% less than children of endogamous White parents. Endogamous children with Hispanic parents and identify as Hispanic earn 10\% less than children of endogamous White parents.

@@

In columns (v) and (vi), I calculate the differences in means between HH-WW (column v) and HW-WH (column vi). Overall, HH children do worse than WW children. HH has one less year of education compared to WW, 2.1 percentage points less likely to be employed, HH men earn 18\% less than WW men, and HH women make 12.3\% less than WW women. Therefore, these two groups, HH and WW, are different in many observable.

@@

Let $Y_{ist}$ be the annual log earnings of person $i$ at time $t$. $WH_{ist}$, $HW_{ist}$ and $HH_{ist}$ are indicator variables for the type of parents person $i$ has. $X_{ist}$ is a vector of controls, $\gamma_{t}$ are year fixed effects, $\lambda_{s}$ are state fixed effects, and $\phi_{ist}$ represents the error term. The equation for this strategy is written as follows:
\begin{equation} \label{eq:1a}
Y_{ist} = \beta_{1} WH_{ist} +\beta_{2} HW_{ist} + \beta_{3} HH_{ist} + X_{ist} \pi + \gamma_{t} + \lambda_s + \phi_{ist}
\end{equation}

@@

Let $Y_{ist}$ be the annual log earnings of person $i$ in state $s$ at time $t$. $WH_{ist}$, $HW_{ist}$ and $WW_{ist}$ are indicator variables for the type of parents person $i$ has. $X_{ist}$ is a vector of controls, $\gamma_{t}$ are year fixed effects, $\lambda_s$ are state fixed effects, and $\phi_{ist}$ represents the error term. The addition to the previous model is the $Hispanic_{ist}$ indicator variable. $Hispanic_{ist}$ is equal to one if a person identifies as Hispanic and zero otherwise. I interact this term with the $WH_{ist}$, $HW_{ist}$ and $HH_{ist}$.  The regression is presented in the following equation.

\begin{align} \label{eq:iden}
Y_{ist} &= \beta_{1} HW_{ist} +  \beta_{2} WH_{ist} + \beta_{3} HH_{ist} +\\
& \beta_{4} WH_{ist} \cdot Hispanic_{ist} + \beta_{5} HW_{ist}\cdot Hispanic_{ist} +  \beta_{6} HH_{ist} \cdot Hispanic_{ist}+ \nonumber \\
&X_{ist} \pi + \gamma_{t} + \lambda_s + \phi_{ist} \nonumber
\end{align}

The coefficients of interest from equation \ref{eq:iden} are $\beta_{4}$, $\beta_{5}$ and $\beta_{6}$. The interaction terms capture the earnings gaps between members of $WH_{ist}$, $HW_{ist}$, and $WW_{ist}$ that identify as Hispanic and White WW children.

@@

I find that the earnings gaps between WH and WW are 14\%, 18\% between HW and WW, and 24\% between HH and WW. Moreover, the difference in earnings between HW and WH children, that captures the effect of having a Hispanic last name, equals a statistically significant 6 percentage points. Meaning by comparing inter-ethnic children, a person with a Hispanic last name earns 6 percentage points less than someone with a White last name. However, more than half of the earnings gaps could be explained by educational differences between WW children and WH, HW, and HH. When I control for education, the gap between the three groups and WW is cut between by 50\% to 64.0\%. Furthermore, the last name effect decreases to a statistically insignificant 2 percentage points earnings gap.

I also find a significant earnings gap between those that identify as Hispanic and WW children. The gaps between WH, HW, and HH that identify as Hispanic and WW are, respectively, 14\%, 18\%, and 10\%. The difference between WH and HW that identify as Hispanic---captures the last name effect of those that identify as Hispanic--- is equal to 3 percentage points and is statistically insignificant. Controlling for education explains a big part of the gap. The gaps between WH, HW, and HH that identify as Hispanic and WW after controlling for education are 8\%, 12\%, and 6\%. The WH--WW and HH--WW gaps for those identifying as Hispanic become statistically insignificant after controlling for education. Finally, the difference between WH and HW that identify as Hispanic that identifies as Hispanic remains statistically insignificant but increases to 4 percentage points.

@@

I provide the results to the estimation of equation \ref{eq:1a} in table \ref{tab:lastnamereg}. The sample in this analysis includes full-time, full-year, and waged and salaried men, and I control for hours worked and age and include year fixed effects (FE). Column one in table \ref{tab:lastnamereg} is the results without controlling for education. Overall, there is big Hispanic--White earnings gaps. Children of White father-Hispanic mothers (WH) earn 14\% less than children of White fathers-White mothers (WW) families. The gap between children of Hispanic father-White mothers (HW) and WW children is 20\%. The gap between children of Hispanic father-Hispanic mothers (HH) and WW children is 24\%. Therefore, Hispanic children, inter-ethnic or children of homogeneous HH marriages, face a substantial earnings gap.

The difference between the estimates of WH and HW would capture the effect of having a Hispanic last name. A WH child will have a White last name since their father is White, while an HW child will have a Hispanic last name like their Hispanic father. When I take the difference between HW and WH, I find a statistically significant gap of 6 percentage points, which means that an inter-ethnic person with a Hispanic last name earns 6 percentage points less than a similar inter-ethnic person but with a White last name.

The literature on the earnings gaps shows that educational differences could explain a big part of these gaps \citep{duncan2006hispanics, duncan2017complexity, duncan2018identifying, duncan2020new}. Therefore, I run the equation \ref{eq:1a}, but this time I control for education. The regression results are in column two of table \ref{tab:lastnamereg}. The sample includes full-time, full-year, and waged and salaried men, and I control for hours worked and age and include year fixed effects (FE). The gap between WH and WW is 9\%, a reduction of 35\% from the baseline after controlling for education. The earning gaps between HW and HH, and WW were respectively reduced by 45\% and 50\%. After controlling for education, an HW man earns 11\% less than a WW man, and an HH man earns 12\% less. The effect of having a Hispanic last name on earnings decreased from 6 to 2 percentage points and became statistically insignificant after controlling for education.

Therefore, Hispanics face big earnings gaps compared to non-Hispanic Whites. By comparing the children of inter-ethnic marriages, I could study the impact of having a Hispanic last name on earnings. Having a Hispanic last name carries a cost in the labor market. A person with a Hispanic last name earns 6 percentage points less than someone with a White name. However, educational differences between Hispanics and Whites could explain more than 50\% of the earning gaps and all of the Hispanic last name costs.

@@

I run the estimating equation without controlling for education in table \ref{tab:identreg} column 1. I find that those that identify as Hispanic face a big earnings gap compared to those that do not. A WH man that identifies as Hispanic earns 14\% less than a WW man. An HW man who identifies as Hispanic makes 18\% less than a WW man, and an HH man who is determined as Hispanic earns 10\% less than a WW man. Comparing the coefficients of the interaction terms to those of the $WH_{ist}$, $HW_{ist}$, and $HH_{ist}$ shows that members of the three groups that do not identify as Hispanic earn about the same as WW.
Moreover, the difference between $HW_{ist} \cdot Hispanic_{ist}$  and $WH_{ist} \cdot Hispanic_{ist}$ captures the effect of having a Hispanic last name and identifying as Hispanic compared to individuals who identify as Hispanic but have a White last name. A person with a Hispanic last name that identifies as Hispanic earns 3 percentage points less than a person that identifies as Hispanic but has a White last name. The difference between the two interaction terms is statistically insignificant.

In table  \ref{tab:identreg} column 2, I show the results of equation \ref{eq:iden} while controlling for education. Education explains all the identity costs for members of WH and HH. Also, controlling for education decreases the earnings gap for identifying as Hispanic and being a member of HW by 33\%. An HW member that identifies as Hispanic earns 12\% less than a WW man. Furthermore, the difference between $HW_{ist} \cdot Hispanic_{ist}$  and $WH_{ist} \cdot Hispanic_{ist}$ increases to 4 percentage points but remains statistically insignificant.

@@

 \begin{equation} \label{eq:naive}
 Y_{ist} = \beta_{1} Hispanic_{ist} + X_{ist}^{\prime} + \gamma_{t} + \lambda_s + \phi_{ist}
 \end{equation}

Where $Y_{ist}$ in equation \ref{eq:naive} is the annual log earnings of person $i$ at time $t$. $Hispanic_{ist}$ is a dummy variable equal to one if person $i$ is Hispanic and zero otherwise. $X_{ist}$ is a vector of controls, $\gamma_{t}$ is time fixed effects and $\phi_{ist}$ is the error term.

@@

I compare the children of inter-ethnic marriages to study the labor market impact of having a Hispanic last name. The earning gap between WH and WW is 14\%, 20\% between HW and WW, and 24\% between HH and WW. When I compare the earnings of HW and WH children, which captures the effect of having a Hispanic last name, HW children earn  6\% less than WH children. Thus, by comparing inter-ethnic children, a person with a Hispanic last name makes 6\% less than someone with a White last name. Controlling for education, however, explains more than half of the earnings gaps between WW children and WH, HW, and HH. When I control for education, the gap between the three groups and WW is cut between 50-64.0\%. Furthermore, the last name effect decreases to a statistically insignificant 2\% earnings gap.

I also find that men who identify as Hispanic earn significantly less than those who do not, even when I control ancestry and education. The gaps between WH, HW, and HH that identify as Hispanic and WW are, respectively, 14\%, 18\%, and 10\%. Controlling for education explains a big part of the gap. The gaps between WH, HW, and HH that identify as Hispanic and WW after controlling for education are 8\%, 12\%, and 6\%.

@@

% $WH_{ist}$ &  & -0.088{*}{*}{*} &  & -0.044{*}{*}{*} & \tabularnewline
%  &  & (0.018) &  & (0.017) & \tabularnewline
%  &  &  &  &  & \tabularnewline
% $HW_{ist}$ &  & -0.141{*}{*}{*} &  & -0.059{*}{*}{*} & \tabularnewline
%  &  & (0.015) &  & (0.014) & \tabularnewline
%  &  &  &  &  & \tabularnewline
% $HH_{ist}$ &  & -0.161{*}{*}{*} &  & -0.058{*}{*}{*} & \tabularnewline
%  &  & (0.008) &  & (0.007) & \tabularnewline
%  &  &  &  &  & \tabularnewline
% \midrule
% $HW_{ist}$ - $WH_{ist}$ &  & -0.053{*}{*} &  & -0.016 & \tabularnewline
%  &  & (0.024) &  & (0.022) & \tabularnewline
%  &  &  &  &  & \tabularnewline
% \midrule
% \textit{Controlling for:} &  &  &  &  & \tabularnewline
% Education &  & No &  & Yes & \tabularnewline
% Hours worked &  & Yes &  & Yes & \tabularnewline
% Age &  & Yes &  & Yes & \tabularnewline
% Year FE &  & Yes &  & Yes & \tabularnewline
% \bottomrule
% \end{tabular}

@@

% \begin{tabular}{lccccc}
% \hline 
%  &  & Log annual earnings &  & Log annual earnings & \tabularnewline
% Variables &  &  &  &  & \tabularnewline
% \hline 
%  &  &  &  &  & \tabularnewline
% $WH_{ist}\times Hispanic_{ist}$ &  & -0.134{*}{*} &  & -0.064 & \tabularnewline
%  &  & (0.053) &  & (0.049) & \tabularnewline
% $HW_{ist}\times Hispanic_{ist}$ &  & -0.164{*}{*}{*} &  & -0.108{*}{*} & \tabularnewline
%  &  & (0.052) &  & (0.048) & \tabularnewline
% $HH_{ist}\times Hispanic_{ist}$ &  & -0.106{*}{*} &  & -0.062 & \tabularnewline
%  &  & (0.049) &  & (0.045) & \tabularnewline
% $WH_{ist}$ &  & 0.027 &  & 0.011 & \tabularnewline
%  &  & (0.048) &  & (0.045) & \tabularnewline
% $HW_{ist}$ &  & 0.007 &  & 0.038 & \tabularnewline
%  &  & (0.050) &  & (0.046) & \tabularnewline
% $HH_{ist}$ &  & -0.057 &  & 0.003 & \tabularnewline
%  &  & (0.057) &  & (0.044) & \tabularnewline
% \hline 
% $HW_{ist}\times Hispanic_{ist}$ - $WH_{ist}\times Hispanic_{ist}$ &  & -0.030 &  & -0.043 & \tabularnewline
%  &  & (0.074) &  & (0.068) & \tabularnewline
% \hline 
% \textit{Controlling for:} &  &  &  &  & \tabularnewline
% Education &  & No &  & Yes & \tabularnewline
% Hours worked &  & Yes &  & Yes & \tabularnewline
% Age &  & Yes &  & Yes & \tabularnewline
% Year FE &  & Yes &  & Yes & \tabularnewline
% \hline 
% \end{tabular}

%   \begin{tablenotes}
%    \item [\textit{Notes.}] This table includes the estimation results of equation \ref{eq:iden}.
%    \item [\textit{Notes.}] The four groups stand for White Husband White Wife (WW), White Husband Hispanic Wife (WH), Hispanic Husband White (HW), and Hispanic Husband Hispanic Wife (HH). $Hispanic_{ist}$ is a dummy variable equal to one if a person identifies as Hispanic and zero otherwise.
%    \item [\textit{Notes.}] The sample is restricted to men working full-time full-year and are waged and salaried workers.
%     \item [\textit{Notes.}] Column one has the regression results when controlling for hours worked, age, and years of fixed effects. Column two has the results after controlling for education.
%   \end{tablenotes}
%   \end{threeparttable}
%   \end{adjustbox}
% \end{table}

@@

% \begin{tabular}{lccccc}
% \hline 
%  &  &  &  &  & \tabularnewline
% Variables &  & Log annual earnings &  & Log annual earnings & \tabularnewline
% \hline 
% $Hispanic_{ist}$ &  & -0.156{*}{*}{*} &  & -0.060{*}{*}{*} & \tabularnewline
%  &  & (0.006) &  & (0.006) & \tabularnewline
% \textit{Controlling for:} &  &  &  &  & \tabularnewline
% Education &  & No &  & Yes & \tabularnewline
% Hours worked &  & Yes &  & Yes & \tabularnewline
% Age &  & Yes &  & Yes & \tabularnewline
% Year FE &  & Yes &  & Yes & \tabularnewline
% \hline 
% \end{tabular}

%   \begin{tablenotes}
%    \item [\textit{Notes.}] This table includes the estimation results of equation \ref{eq:naive}.
%    \item [\textit{Notes.}] $Hispanic_{ist}$ is a dummy variable equal to one if a person identifies as Hispanic and zero otherwise.
%    \item [\textit{Notes.}] The sample is restricted to men working full time full-year and are waged and salaried workers.
%     \item [\textit{Notes.}] Column one has the regression results when controlling for hours worked, age, and fixed effects. Column two has the results after controlling for education.
%   \end{tablenotes}
%   \end{threeparttable}
%   \end{adjustbox}
% \end{table}
